Supplementary Materials

### 2020-06-05 analysis/analysis.Rmd
updated subgroup table

glimpse(subgroups)

@@

sym_dat %>% pivot_longer(-group, names_to = "symmetry", values_to = "order") %>%
  ggplot(aes(x = symmetry, y = order, fill = as.factor(order))) + geom_col() + facet_wrap(~ group) +
  theme_bw() + 
  scale_y_continuous(breaks = c(2,4,6)) + 
  ggthemes::scale_fill_ptol() + 
  theme(
    panel.grid.minor=element_blank(), 
    legend.position = "none")

>>>>

@@

knitr::kable(sym_dat, caption = "wallpaper group summary", escape = "F") %>% kableExtra::kable_styling(full_width = F)
